Make any stupid plot you want

### 2021-01-07 draft/sections/implementation.tex
going in circles here
start of implementation

\documentclass[../main.tex]{subfiles}
\begin{document}

\subsection{Data Model}

>>>>

\documentclass[../main.tex]{subfiles}
\begin{document}
\section{Matplottoy}
\begin{figure}
\includegraphics[width=\linewidth]{figures/sections/math/path_of_q.png}
\end{figure}
%%% objects: Data, V, H
%%% functions: \nu, q

We build on top of the existing Matplotlib architecture \cite{hunterMatplotlib2DGraphics2007} so that we can initially focus on the data to graphic transformations and rely on Matplotlib for the other graphical elements of the visualization and the rendering. For a primitive graph such as a bar, scatter, line, our path is: 
\begin{minted}{python}

E = Section()
V = {'parameter': ('field': transformer)}

fig, ax = plt.subplots()
artist = primative_Q(E, V)
ax.add_artist(artist)
\end{minted}

\subsection{Data: $\mathcal{E}$}
We propose a semantic markup of the fiber and connectivity that we will later use to check the constraints of the $\nu$ and $Q$. 
\begin{minted}{python}
class FiberBundle:
    def __init__(self, K, F):
            """
            K: {'tables':[]}
            F: {'field name': (type, monoid action)}
            """

    def is_section(self, section):
        """checks if a section is from a given fiber bundle:
        are values in F, are keys in K"""
\end{minted}
We add a monoid field to the schema like structure of the fiber since the monoid actions are the constraints on the $\nu$ and $Q$. We implement $K$ using the triangulization scheme described in section~\ref{sec:triangulization}. This means we expect data to be provided as tables where the name encodes the connectivity:

\begin{description}
    \item[vertex] - disconnected points
    \item[edge] - 1D continuity along the edge
    \item[face] - 2D continuity along the face
\end{description}
Nested continuity is encoded in the fiber. For example, one way to encode a movie is a 1D timeseries of \mathrm{Frame} objects, where each \mathrm{Frame} is a $n\x m$ continuous array.

\subsubsection{Sections}
As described in section~\ref{sec:section_data}, the data values are encode as the section of the fiber bundle. We implement this as as a wrapper class around a data container object of the form:
\begin{minted}
class Section:
    FB = FiberBundle(K, F)

    def __init__(self, *args):
        pass
    def view(self, simplex="vertex"):
        """"converts data into atomic column order for get method
        # maybe also pass in the columns?
        """
        return {fieldname: data}
\end{minted}

The view function is the closest analog to $\tau$, as it returns a a data container type object. We specify field based top level indexing so that we can pair the fields with transformer $\nu$ objects.

\subsection{Encoding: $\mathcal{V}$}
We implement $\nu$ as encoder objects with an optional `__init__` method that can be used to specify the range of target visual variables.

\begin{minted}{python}
class Encoder:
    def __init__(self, args):
        pass
    def validate(self, monoid):
        pass
    def convert(self, value):
        return converted_value
\end{minted}

The \mathrm{validate} method specifies the monoids for which this a valid $\nu$ and checks against the specification in the fiber. The \mathrm{convert} method converts a value from data space to an internalized normal form as described in table~\ref{tab:mpl_visual_variable_fiber}.

\subsection{Graphic: $\mathcal{H}$}

\subsection{Case Study: Iris(Penguins)}
